Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-24 article.tex
Adde mike garay in correct style.

@@

\author{Amit~Aides and Yoav~Y.~Schechner and Vadim~Holodovsky}

\address{Electrical Engineering Dept., Technion - Israel Inst. Tech., \\ Haifa 32000, Israel}

\email{amitibo@tx.technion.ac.il} %% email address is required

>>>>

\newcommand\authnote[1]{\textsuperscript{\normalfont#1}}
\newcommand\affilnote[1]{\textsuperscript{\normalfont#1}}
\providecommand\textsuperscript[1]{$^{#1}$}

@@

\author{Amit~Aides,\authnote{1*} Yoav~Y.~Schechner,\authnote{1} Vadim~Holodovsky\authnote{1} and Michael~J.~Garay\authnote{2}}

\address{\affilnote{1}Electrical Engineering Department, Technion - Israel Institute of Technology, Haifa 32000, Israel\\
\affilnote{2}Jet Propulsion Laboratory, California Institute of Technology, Pasadena, CA 91109, USA}

\email{\authnote{*}amitibo@tx.technion.ac.il} %% email address is required
